NMRlipids Databank: Overlay Databank of Lipid Membrane Simulations Arising from Open Collaboration

### 2022-11-02 main.tex
Add flip-flop figure

\begin{figure}[tb]
    \centering
    \includegraphics[width=180mm]{Figures/permeation2.pdf}
    \caption{A 
    {\bf B-E} Water permeation through membranes analyzed from the databank as a function of temperature, thickness, area per lipid, and acyl chain order. Values from simulations with non-zero permeation values are shown with blue dots. Averages over fixed range of x-axis values are shown with black dots. Insert in B) shows the Arrhenius plot of permeation ($\ln$ (P) vs. 1/T) that gives 17\,$\pm$\,4\,k$_b$T for the average activation energy for water permeation through lipid bilayer. Inserts in C) and D) show the region where the dependence could be considered approximately linear.
    {\bf F} Lateral diffusion of water as a function of hydration level. Experimental points for DMPC bilayers at 313\,K at different hydration levels are shown~\cite{rudakova04}.
    {\bf G-H} Diffusion anistoropy of water as a function of thickness and area per lipid. }
    \label{fig:permeability}
\end{figure}

@@

>>>>

\begin{figure}[tb]
    \centering
    \includegraphics[width=180mm]{Figures/permeation2.pdf}
    \caption{{\bf A} Water diffusion, $D_\perp$, and permeability, $P$, through membranes, and lateral diffusion along the membrane, $D_{||}$, illustrated in a multilamellar stack of lipid bilayers. 
    {\bf B-E} Water permeation through membranes analyzed from the databank as a function of temperature, thickness, area per lipid, and acyl chain order. Values from simulations with non-zero permeation values are shown with blue dots. Averages over fixed range of x-axis values are shown with black dots. Insert in B) shows the Arrhenius plot of permeation ($\ln$ (P) vs. 1/T) that gives 17\,$\pm$\,4\,k$_b$T for the average activation energy for water permeation through lipid bilayer. Inserts in C) and D) show the region where the dependence could be considered approximately linear.
    {\bf F} Lateral diffusion of water as a function of hydration level. Experimental points for DMPC bilayers at 313\,K at different hydration levels are shown~\cite{rudakova04}.
    {\bf G-H} Diffusion anistoropy of water as a function of thickness and area per lipid. }
    \label{fig:permeability}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=88mm]{Figures/CholFlipFlops.pdf}
    \caption{{\bf A} Illustration of cholesterol flip-flop.  
      {\bf B-D} Cholesterol flip-flops analyzed from the databank as a function of membrane thickness, area per lipid, and acyl chain order.
      Values from simulations with non-zero flip-flop rates are shown with blue dots. Averages over fixed range of x-axis values are shown with black dots.
    }
    \label{fig:permeability}
\end{figure}
